Initial Analysis

### 2019-08-30 Initial_Analysis.Rmd
Updates to the find neighbour method. hopefully faster

```{Tran_country_Map_All, eval =F, echo =F}

@@

>>>>

### Maps for each model/dataset
```{Tran_country_Map_All, eval =F, echo =F}

@@

### RFMO analysis

```{r Find_Neighbours_sf, eval = F, echo =F}

#load North Carolia Data from sf
nc <- st_read(system.file("shape/nc.shp", package="sf"), quiet = TRUE)

# Get sparse matrix
int = st_intersects(nc)

# Intitalize new object
mat = NULL

# Fill
for(i in 1:NROW(int)){
  #Create matrix with ID and intersecting IDs
  tmp = cbind(i, int[[i]])
  # Join to Initalized object
  mat  = rbind(mat, tmp)
}

# Build final data.frame substituting ID for name (in this case nc$name)
matrix = data.frame(country = nc$NAME[mat[,1]], neighbor = nc$NAME[mat[,2]] )

# Remove duplicates... eg of course an object intersects with itself...
matrix = matrix[matrix$country != matrix$neighbor,]

# Check it out, 
head(matrix)
